---
title: "Regional Labor Markets and the Politics of Resentment"
subtitle: "Regional unemployment risks, inter-regional relocation, and anti-immigration sentiment"
author:  
  <table class="authors">
    <tbody>
      <tr>
        <td>Denis Cohen</td>
        <td>Sergi Pardos-Prado</td>
      </tr>
      <tr>
        <td>.font75[University of Mannheim]</td>
        <td>.font75[University of Glasgow]</td>
      </tr>
    </tbody>
  </table>
  <table class="contact">
    <tbody>
      <tr>
        <td>`r icon::fa("envelope")` [`denis.cohen@mzes.uni-mannheim.de`](mailto:denis.cohen@mzes.uni-mannheim.de)</td>
        <td>`r icon::fa("envelope")` [`sergi.pardos-prado@glasgow.ac.uk`](mailto:sergi.pardos-prado@glasgow.ac.uk)</td>
      </tr>
      <tr>
        <td>`r icon::fa("globe")` [`denis-cohen.github.io`](https://denis-cohen.github.io)</td>
        <td>`r icon::fa("globe")` [`sergipardos.wixsite.com`](https://sergipardos.wixsite.com/)</td>
      </tr>
      <tr>
        <td>`r icon::fa("twitter")` [`@denis_cohen`](https://twitter.com/denis_cohen)</td>
        <td>`r icon::fa("twitter")` [`@sergipardos`](https://twitter.com/sergipardos)</td>
      </tr>
    </tbody>
  </table>
  
date: 
  Humboldt Political Behavior Workshop <br /> September 10, 2021
  
output: 
  xaringan::moon_reader:
    includes:
      after_body: insert-logo.html
    css:
      - default
      - mtheme2.css
      - fonts_mtheme.css
    nature: 
      beforeInit: "macros.js"
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: '16:9'
      slideNumberFormat: |
        <div class="progress-bar-container">
          <div class="progress-bar" style="width: calc(%current% / %total% * 100%);">
          </div>
        </div>
    class: inverse, mline, center, middle
---

```{r setup, include=FALSE}
## Save package names as a vector of strings
pkgs <-
  c("rmarkdown",
    "knitr",
    "dplyr",
    "devtools",
    "widgetframe",
    "RefManageR",
    "bibtex",
    "bib2df",
    "plotly",
    "magick",
    "kableExtra")

## Install uninstalled packages
lapply(pkgs[!(pkgs %in% installed.packages())], install.packages)

## Load all packages to library and adjust options
lapply(pkgs, library, character.only = TRUE)

## Devtools install
if (!("icon" %in% installed.packages()))
  devtools::install_github("ropenscilabs/icon")
library(icon)

## Global chunk options
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = TRUE)
options(scipen=999)
options(htmltools.dir.version = FALSE)

## RefManageR options
BibOptions(
  bib.style = "authoryear",
  hyperlink = "to.bib",
  style = "markdown",
  max.names = 3L
)

# ---- Functions ----Function
load_data <- function(file_name){
    load(file_name)
    get(ls()[ls() != "file_name"])
}
```

```{r flex-bib, eval=FALSE, cache=FALSE, include = FALSE}
## ---- Copy bib files into repository ----
## Copy Denis' synced bib file
if (Sys.info()["user"] %in% c("denis", "dcohen", "homeoffice")) {
  file.copy(from = "../../../../library.bib",
            to = "../tex/bib/denis.bib",
            overwrite = TRUE)
}

## ---- Run flex_bib ----
## Source function
source_url(
  "https://raw.githubusercontent.com/paulcbauer/flex_bib/master/flex_bib.R"
  )

## Main text
flex_bib(
  rmarkdown_file = c(
    "../tex/01_00_introduction.Rmd",
    "../tex/02_00_theory.Rmd",
    "../tex/03_00_empirical_strategy.Rmd",
    "../tex/04_00_findings.Rmd",
    "../tex/05_00_summary_and_discussion.Rmd"
  ),
  bib_input = c("../tex/bib/denis.bib", "../tex/bib/sergi.bib"),
  bib_output = "bib/main.bib",
  repair = TRUE,
  removeISSN = TRUE,
  removeISBN = TRUE,
  removeDOI = TRUE,
  removeURL = TRUE
)
```

```{r refmanager}
## Read bib file
bib <- RefManageR::ReadBib("bib/main.bib", check = FALSE)
```

# In a nutshell

### What we know: Anti-immigration sentiment is regionally clustered

--

- Regional economic contexts and the socio-economic composition of regions correlate with anti-immigration sentiment
--

- These patterns are (partly) driven by residential self-selection `r Citep(bib, "Maxwell2019", before = "e.g., ")`

--
- But the mechanism underlying these selection processes remain understudied

--

### What we show: Regional heterogeneity in labor demand matters

--

- Prospects of living in a region with higher labor demand predict individual moving decisions (but only if skills are sufficiently transferable)
--

- Intra-individual reductions in unemployment risks alleviate concerns about immigration, especially when driven by self-selection into better regional labor markets
--

- Macro-level implications: Higher share of risk-reducing movers in a region predicts aggregate anti-immigration sentiment, over and beyond a host of structural factors


---

class: inverse, mline, center, middle

# Theory

---

# Motivation

### Increasing interest in the political consequences of regional disparities

- Rural/urban residence and immigration preferences .cyan[(van Heerden and Ruedin 2019; Maxwell 2019, 2020; Huijsmans et al. 2021)]
- Residential sorting and political homophily .cyan[(Gallego et al. 2014, Martin and Webster 2020)]
- Local conditions and far-right voting .cyan[(Golder 2016; Harteveld et al. 2021)]
- Housing markets and political behavior .cyan[(Ansell and Adler 2019; Ansell et al. 2019; Dancygier and Chou 2021)]
- Regional economies and political backlash .cyan[(Colantone and Stanig, 2018a,b; Carreras, Carreras and Bowler 2019; Fetzer 2019; Broz et al. 2021)]

--

### Persistent interest in economic explanations of immigration preferences

- Supply-side theories of ethnic labor market competition .cyan[(Hainmueller and Hiscox 2007, 2010; Malhotra, Margalit and Mo 2013; Hainmueller, Hiscox and Margalit 2015)]
- Demand-side theories .cyan[(Dancygier and Donnelly 2013; Pardos-Prado and Xena 2019)]


---

# Argument I

.cyan[Heterogeneity in regional labor markets explains inter-regional residential relocation]

--

### Mechanism

- Regional-occupational .cyan[labor demand] (low unemployment risk) is an important pull factor:
    - prospects of increased income
    - prospects of occupational upgrading
    - prospects of better job security (medium term)
--
- Individuals are more likely to follow these incentives when:
    - they anticipate relative improvements in their labor market standing
    - their skills are sufficiently transferable

---

# Argument II

.cyan[The economic mechanisms that drive inter-regional relocation concurrently affect anti-immigration sentiment]

--

### Mechanism

- The underlying mechanism is once again .cyan[labor demand] (low unemployment risk)
- Over and beyond immigrant labor supply, varying levels of job availability and job security affect economic opposition to immigration `r Citep(bib, "Pardos-Prado2018")`

--

### Open questions

- Are .cyan[exogenous] changes in unemployment risks (due to labor market volatility) equi-effective to comparable .cyan[endogenous] changes (due to occupational change or relocation)?
- Do changes in unemployment risks affect those with and without experiences of moving/a propensity to move equally?

---

# Expectations

### Explaining inter-regional residential relocation

<blockquote>
  H1: Individuals are more likely to move inter-regionally when they face lower unemployment risks in their new region of residence than in their previous one.
  </br></br>
  H2: Individuals are more likely to move inter-regionally when they face lower unemployment risks in their new region of residence than in their previous one, provided their skills are sufficiently transferable (conditional effect).
</blockquote>

--

### Explaning anti-immigration sentiment

<blockquote>
  H3: The higher the unemployment risk an individual is exposed to, the greater their concern about immigration (micro-level).
  </br></br>
  H4: The higher the regional proportion of inter-regional risk-reducing movers, the lower the aggregate level of anti-immigration concerns (macro-level).
</blockquote>

---

class: inverse, mline, center, middle

# Data

---

# A new data set on German regions, 1996-2019

### Data set

- Based on representative aggregations from the .cyan[German microcensus]
    - annual interviews of 1% of the German residential population (~810,000 interviews p.a.)
    - operated by the Federal Statistical Office (DESTATIS) since 1957
--
- Annual data at the level of German RAS regions (145 regions à ~500,000 residents)
- Direct linkage to administrative entities (counties, cities)

--

### Variables

- .cyan[demographic composition] (avg. age, % female, % foreign-born, % homeowners)
- .cyan[labor market characteristics] (% active, % unemployed, % job changers, qualifications)
- .cyan[occupation-specific information] (prevalence, unemployment risk)


---

# Micro-level panel data: GSOEP, 1999-2017

### Data set

- annual georeferenced panel data at the individual and household levels (restricted access)
- supplemented with our regional context data using county and city IDs

--

### Variables

- .cyan[Inter-regional residential relocation]: $\text{county}_{t} \neq \text{county}_{t-1}$
--

- .cyan[Worries about immigration] (generalized anti-immigration sentiment)
--

- .cyan[Regional-occupational unemployment risk dynamics] (structured by Oesch-8 classes)
--

- .cyan[Absolute skill specificity] `r Citep(bib, "Iversen2001")`

---

# Regional unemployment risks

```{r risk, fig.width=8, fig.height=6, out.width="100%", fig.cap="Note: Regional-occupational unemployment risks by Oesch classes."}
magick::image_read_pdf("../fig/2021_06_06_descriptives/ras_risk_oesch8.pdf",
                       pages = 1)
```

---

class: inverse, mline, center, middle

# Analyses

---

# Micro-level panel analyses

- Within-between models with additional random intercepts for households, counties, and states
- Ran across five multiply imputed data sets, using cross-sectional sampling weights
--

### Specifications

1. $\text{Inter-regional move}_{i, t} = f(\text{risk}_{i,t}, \text{risk}_{i,t-1}, \text{controls})$
1. $\text{Inter-regional move}_{i, t} = f(\text{risk}_{i,t}, \text{risk}_{i,t-1}, \text{skill specifity}_{i,t-1}, \text{controls})$
1. $\text{Worries about immigration}_{i, t} = f(\text{risk}_{i,t}, \text{risk}_{i,t-1}, \text{controls})$ (subsets)
--

### Controls

- education, age, number of household members
- unemployment at $t-1$ and $t$
- East/West residence, residence in rural, suburban, or urban places, regional mean age, regional proportion of foreign-born residents (all at $t-1$ and $t$)
- (imputed) rents $\times$ homeownership at $t-1$, income and occupation (at $t-1$ and $t$)


---

# Aggregate-level analysis

- Cross-sectional analysis at the level of 401 counties (2017 boundaries)
- Pooled information over time (1999-2017)

--

### Key variables

- Aggregate-level anti-immigration sentiment in county $j$
- Average proportion of inter-regional risk-reducing movers in county $j$
- Both estimated from survey data using a global smoothing approach via multi-level regression with county-level predictors

--

### Controls

- Avg. unemployment risk
- Avg. annual change in unemployment risk
- East/West
- Rural/suburban/urban




---

class: inverse, mline, center, middle

# Findings

---

# Risk and inter-regional relocation

```{r 04-data-objects}
## Objects
files <- list.files("../est")
rmd_files <- files[substr(files, nchar(files) - 5L, nchar(files)) == ".RData"]
est <- lapply(paste0("../est/", rmd_files), load_data)
names(est) <- substr(rmd_files, 1L, nchar(rmd_files) - 6L)

## Hypothetical risk shift 
risk_shift <- -0.05
```

```{r irm1, fig.width=6, fig.height=4, out.width="50%", fig.cap="Note: Within-effects of a five percentage-point decrease in region-occupational unemployment risk on inter-regional residential relocations.", fig.align = 'center', dpi = 600}
## Temporary estimates
est_tmp <- est[["20210604_wb_irm"]]

## Aux
model_groups <- rep(1:9, each = 18)
last_outcome <- "none"
is_discrete <- FALSE

## Estimates
group_select <- 8L
spec_select <- 11L
effect_select <- "within"

tmp <- est_tmp[model_groups %in% group_select][spec_select] %>%
  sapply(function(x)
    x$effects[, "within"]) * risk_shift * 100

## y-limits
y.lim <- y.range <- c(0, 4)
y.coarse <- ceiling(abs(diff(y.range))) / 2


## Plot
par(mar = c(0, 7.1, 1.1, 1.1),
    oma = c(0, 0, 0, 0),
    mfrow = c(1, 1))
plot(
  seq_along(ncol(tmp)),
  seq_along(ncol(tmp)),
  xlim = c(.5, ncol(tmp) + .5),
  ylim = y.lim,
  type = 'n',
  axes = F,
  xlab = "",
  ylab = "Marginal within-effect of a \n 5pp decrease in unemployment risk"
)
axis(2)
abline(
  h = seq(y.lim[1], y.lim[2], 1),
  col = 'gray75',
  lwd = .3,
  lty = 3
)
abline(
  v = seq_len(ncol(tmp)),
  col = 'gray75',
  lwd = .3,
  lty = 3
)
abline(h = 0,
       col = 'red',
       lwd = 1)
axis(2)

segments(1, tmp[2, 1], 1, tmp[3, 1], lwd = 2, lend = 2)
points(
  1,
  tmp[1, 1],
  pch = 21,
  col = "black",
  bg = "black",
  cex = 2
)
```


---

# Risk and inter-regional relocation

```{r irm2, fig.width=9, fig.height=4, fig.align = 'center', out.width="75%", fig.cap="Note: Conditional within-effects of a five percentage-point decrease in region-occupational unemployment risk on inter-regional residential relocations as a function of absolute skill specificity.", dpi = 600}
## Temporary estimates
est_tmp <- est[["20210604_wb_irm"]]

## Aux
model_groups <- rep(1:9, each = 18)
last_outcome <- "none"
is_discrete <- FALSE
plot_titles <-
  "Marginal within-effect of a \n 5pp decrease in unemployment risk"

## Plot
par(
  mfrow = c(1, 1),
  mar = c(0.25, 5.1, 0, 0),
  oma = c(5.1, 0.1, 0, 0)
)

for (p in seq_along(plot_titles)) {
  if (p == 1) {
    group_select <- 9L
    spec_select <- 11L + c(0:2) * 18L
    effect_select <- "within"
    
    tmp <- est_tmp[model_groups %in% group_select][spec_select][[1]]
    tmp$effects$within <- tmp$effects$within * risk_shift * 100
  } else if (p == 2) {
    group_select <- 9L
    spec_select <- 17L + c(0:2) * 18L
    effect_select <- "within"
    
    tmp <- est_tmp[model_groups %in% group_select][spec_select][[1]]
    tmp$effects$within <- tmp$effects$within * risk_shift * 100
  }
  
  ## Within-range
  within_range <- c(-8, 6)
  
  ## Moderator information
  vals <- seq(
    min(tmp$moderator$cut),
    max(tmp$moderator$cut),
    length.out = length(tmp$moderator$cut)
  )
  
  dist <- tmp$moderator$val
  within_dist  <-
    (dist / max(dist)) * (0.9 * diff(within_range)) + min(within_range)
  
  ## Setup
  plot(
    1,
    1,
    xlim = range(vals) + c(-.1, .1) * diff(range(vals)),
    ylim = within_range,
    type = "n",
    pch = 19,
    xlab = "",
    ylab = "",
    main = "",
    axes = F,
    
  )
  
  ## Moderator distribution
  for (k in 1:(length(vals) - 1L)) {
    rect(
      vals[k],
      min(within_range),
      vals[k + 1],
      within_dist[k],
      col = adjustcolor("gray60", alpha.f = 0.2),
      border = NA
    )
  }
  
  ## Grid lines
  abline(
    h = seq(-8, 6, 2),
    col = 'gray75',
    lwd = .3,
    lty = 3
  )
  abline(
    v = seq(0, .5, .1),
    col = 'gray75',
    lwd = .3,
    lty = 3
  )

  ## Reference line
  if (prod(within_range) <= 0) {
    segments(
      min(vals) - .1 * diff(range(vals)),
      0,
      max(vals) + .1 * diff(range(vals)),
      0,
      col = "red",
      lwd = .25
    )
  }
  
  ## Estimates
  segments(vals,
           tmp$effects$within[2,],
           vals,
           tmp$effects$within[3,],
           lwd = .5)
  points(vals,
         tmp$effects$within[1,],
         pch = 19,
         cex = .5)
  
  ## Axes
  axis(2, outer = F)
  axis(1, outer = T)

  ## Box
  box()
  
  ## Side titles
  title(ylab = plot_titles[p], outer = F)
}
title(xlab = "Absolute Skill specificity", outer = TRUE)
```

---

# Risk, relocation & anti-immigration sentiment

```{r wim, fig.width=9, fig.height=3, out.width="100%", fig.cap="Note: Within-effects of a five percentage-point decrease in region-occupational unemployment risk on anti-immigration concerns.", fig.align='center', dpi = 600}
## Temporary estimates
est_tmp <- est[["20210605_wb_wim"]]

## Aux
model_groups <- c(
  rep(1L, 24L),
  rep(2L, 24L),
  rep(3L, 24L),
  rep(4L, 18L),
  rep(5L, 18L),
  rep(6L, 24L),
  rep(7L, 24L),
  rep(8L, 24L),
  rep(9L, 18L),
  rep(10L, 18L),
  rep(11L, 24L),
  rep(12L, 24L),
  rep(13L, 24L),
  rep(14L, 18L),
  rep(15L, 18L)
)
last_outcome <- "none"
is_discrete <- FALSE

## Plot
est.nms <- c(
  "Samples",
  "Full sample",
  "Never moved inter-regionally while in sample",
  "Moved inter-regionally while in sample"
)
plot_titles <-
  "Marginal within-effect of a \n 5pp decrease in unemployment risk"
widths <- c(4, 4)
breaks <- rep(0.5, length(widths))
breaks2 <- rep(0.5, length(widths) - 1L)
for (i in seq_along(widths)) {
  breaks[i + 1] <- breaks[i] + widths[i]
}
for (i in seq_along(breaks2)) {
  breaks2[i + 1] <- breaks2[i] + (widths[i] - 1L)
}

## Layout
m2by2 <-  rbind(c(rep(1, 4), rep(2, 2)))
layout(m2by2)
par(oma = c(5.1, 0, 0, 0))

for (p in seq_along(plot_titles)) {
  if (p == 1) {
    group_select <- 12L
    spec_select <- 13:15
    effect_select <- "within"
    
    tmp <- est_tmp[model_groups %in% group_select][spec_select] %>%
      sapply(function(x)
        x$effects[, "within"]) * risk_shift

  } else if (p == 2) {
    group_select <- 12L
    spec_select <- 21:23
    effect_select <- "within"
    
    tmp <- est_tmp[model_groups %in% group_select][spec_select] %>%
      sapply(function(x)
        x$effects[, "within"]) * risk_shift
  }
  
  y.lim <- y.range <- c(-.08, 0)
  y.coarse <- ceiling(abs(diff(y.range))) / 2
  
  par(mar = c(0, 7.1, 1.1, 1.1))
  plot(
    seq_along(ncol(tmp)),
    seq_along(ncol(tmp)),
    xlim = c(.5, ncol(tmp) + .5),
    ylim = y.lim,
    type = 'n',
    axes = F,
    xlab = "",
    ylab = plot_titles[p]
  )
  axis(
    1,
    labels = 1:ncol(tmp),
    at = 1:ncol(tmp),
    outer = TRUE,
    cex.axis = 1
  )
  abline(
    h = seq(y.lim[1], y.lim[2], .02),
    col = 'gray75',
    lwd = .3,
    lty = 3
  )
  abline(
    v = seq_len(ncol(tmp)),
    col = 'gray75',
    lwd = .3,
    lty = 3
  )
  abline(h = 0,
         col = 'red',
         lwd = .3)
  axis(2)
  
  # ## Boxes
  # for (u in 1:(length(breaks2) - 1)) {
  #   rect(
  #     breaks2[u] + .1,
  #     y.lim[1],
  #     breaks2[u + 1] - .1,
  #     y.lim[2],
  #     col = adjustcolor("gray70", alpha.f = .2),
  #     border = NA
  #   )
  # }
  
  ## Estimates
  for (j in 1:ncol(tmp)) {
    segments(j, tmp[2, j], j, tmp[3, j], lend = 2)
    points(
      j,
      tmp[1, j],
      pch = 21,
      col = "black",
      bg = "black",
      cex = 1
    )
  }
}
## Plot 4
par(mar = c(0.1, 0.1, 0.1, 0.1))
plot(
  seq_along(ncol(tmp) - 1),
  seq_along(ncol(tmp) - 1),
  ylim = c(mean(c(max(breaks), max(breaks2))) - 1.75, 0),
  xlim = c(0, 10),
  type = 'n',
  axes = F,
  xlab = "",
  ylab = ""
)

## Title
text(0, 0, "Legend", pos = 4, cex = 1)

## Boxes
for (u in 1:(length(breaks) - 2)) {
  rect(
    0.1,
    (breaks[u] + .1),
    9.9,
    (breaks[u + 1] - .1),
    col = adjustcolor("gray70", alpha.f = .2),
    border = NA
  )
}
k = 0L
for (u in seq_along(est.nms)) {
  is.title <- ifelse(any(u - breaks == 0.5), TRUE, FALSE)
  if (is.title) {
    text(0.1, u, est.nms[u], cex = 1, pos = 4)
  } else {
    k = k + 1L
    points(0.75,
           u,
           pch = 21,
           bg = "white",
           cex = 3.25)
    text(0.75, u, k, cex = 1)
    text(
      1.25,
      u,
      est.nms[u],
      font = ifelse(u %in% c(1, cumsum(widths[1:(length(widths) - 2)]) + 1),
                    2,
                    1),
      pos = 4,
      cex = 1
    )
  }
}
```

---

# County-level anti-immigration sentiment

```{r}
tab <- read.csv("../tab/2021_06_05_aggregate/prop_irrr_movers.csv") %>%
  dplyr::select(-`Model.1`, -`Model.2`)
colnames(tab) <- c("", paste0("Model ", 1:4))
tab <- tab[c(7:8, 3, 5, 9, 11, 13), ]
for (j in 3:nrow(tab)) {
  for (k in 2:ncol(tab)) {
    tab[j, k] <- ifelse(tab[j, k] == "", "", "incl.")
  }
}
knitr::kable(tab, 
             format = 'html',
             align = c("l", "c", "c", "c", "c"),
             row.names = FALSE,
             caption = "Note: OLS estimates based on 401 German counties.")
```

---

class: inverse, mline, center, middle

# Summary and conclusion

---

# Summary and conclusion

<!-- -- -->

- Inter-regional discrepancies in occupational labor market conditions create incentives for residential relocation
--

- Improving one's labor market situation through moving results in intra-individual reductions in anti-immigration sentiment; this implies economically driven context-plus-composition effects
--

- At the aggregate-level, this not only helps us understand the formation of occupational-sectoral clusters but also the formation of "immigration sentiment clusters"
--

- Heterogeneity in regional labor markets and residential sorting are thus important mechanisms that help us better understand
    - intra-individual dynamics in the formation of anti-immigration sentiment
    - the subnational political geography of anti-immigration sentiment


---


class: inverse, center, middle,title-slide

# Thank you!

## Your feedback is highly appreciated.

### <table class="authors">
<tbody>
<tr>
<td>Denis Cohen</td>
<td>Sergi Pardos-Prado</td>
</tr>
<tr>
<td>.font75[University of Mannheim]</td>
<td>.font75[University of Glasgow]</td>
</tr>
</tbody>
</table>
<table class="contact">
<tbody>
<tr>
<td>
<i class="fas  fa-envelope "></i> <a href="mailto:denis.cohen@mzes.uni-mannheim.de"><code>denis.cohen@mzes.uni-mannheim.de</code></a>
</td>
<td>
<i class="fas  fa-envelope "></i> <a href="mailto:sergi.pardos-prado@glasgow.ac.uk"><code>sergi.pardos-prado@glasgow.ac.uk</code></a>
</td>
</tr>
<tr>
<td>
<i class="fas  fa-globe "></i> <a href="https://denis-cohen.github.io"><code>denis-cohen.github.io</code></a>
</td>
<td>
<i class="fas  fa-globe "></i> <a href="https://sergipardos.wixsite.com/"><code>sergipardos.wixsite.com</code></a>
</td>
</tr>
<tr>
<td>
<i class="fab  fa-twitter "></i> <a href="https://twitter.com/denis_cohen"><code>@denis_cohen</code></a>
</td>
<td>
<i class="fab  fa-twitter "></i> <a href="https://twitter.com/sergipardos"><code>@sergipardos</code></a>
</td>
</tr>
</tbody>
</table>